Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-19 paper/Paper.tex
Generic > Standard

This paper presents a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality. This paper illustrates a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2)  governance rules are formalized, automated and enforced using software. Specifically, generic smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. This paper explains how a DAO's code works, focusing on some basic formation and governance features, including structure, creation and voting rights.

>>>>

This paper presents a potential solution using Ethereum, (\cite{buterin2013ethereum,Wood2014ethereum}) a blockchain technology which integrates a Turing complete programming language with smart contract processing functionality. This paper illustrates a method that for the first time allows the creation of organizations in which (1) participants maintain direct real-time control of contributed funds and (2)  governance rules are formalized, automated and enforced using software. Specifically, standard smart contract code (\cite{szabo1997formalizing, miller1997future}) has been written that can be used to form a Decentralized Autonomous Organization (DAO) on the Ethereum blockchain. This paper explains how a DAO's code works, focusing on some basic formation and governance features, including structure, creation and voting rights.
